Storing messages with multipartite neural cliques

### 2014-07-01 Articles/article.tex
réorganisation
Ajout courbe
///
...

	 \begin{abstract}
	 	We extend recently introduced associative memories based on cliques to multipartite cliques. We propose a variant of the classic retrieving rule. We study their relative performance for retrieving partially erased and corrupted messages. We provide both analytical and simulation results showing improvements of capacity.
	 \end{abstract}

@@

@@

@@

	% À corriger avec sommes multiparties
	%\[P(\mbox{no other vertex activated in this cluster})= \sum_{n_0 = 1}^{a c_k} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a } \]

	%\[P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n_0 = 1}^{a c_k} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}\]

@@

		a priori for noise on edges :

	\[P(\mbox{no other vertex activated in this cluster})= \sum_{n = 1}^{a c_k} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] \left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a } \]

	\[P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n = 1}^{a c_k} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] \left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}\]

@@

	Formula for errors insted of erasures :

>>>>

	 \begin{abstract}
	 	We extend recently introduced associative memories based on cliques to multipartite cliques. We propose a variant of the classic retrieving rule. We study their relative performance for retrieving partially erased and corrupted messages. We provide both analytical and simulation results showing improvements of capacity over.
	 \end{abstract}

@@

	$\eta_m = (P_{retrieve} m ) \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times \frac{c}{(c-c_e) \log_2{l \choose a }}$

	$\eta_{max} = \max_x \eta_x $

@@

		\begin{figure}
		\includegraphics[width=8.5cm]{remplacement_figure4g1}
		\caption{Comparison between different number of activities per cluster :  4 clusters, 512 neurons per cluster, 1000 sampled messages}
	\end{figure}

@@

	% À corriger avec sommes multiparties
	%$P(\mbox{no other vertex activated in this cluster})= \sum_{n_0 = 1}^{a (c - c_e)} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a}$

	%$P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n_0 = 1}^{a ( c - c_e)} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}$

@@

		a priori for noise on edges :
	\newpage
	l
	\newpage
	$P(\mbox{no other vertex activated in this cluster})= \sum_{n = 1}^{a (c - c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] \left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a }$

	$P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n = 1}^{a ( c- c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] \left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}$

@@

	Formula for errors instead of erasures :
